Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-13 paper/reviewers-response.Rmd

\doublespacing

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
```

We are thankful to the assistant editor James Ross, the senior editor and David Gibson, and three anonymous reviewers for the insightful comments to improve the manuscript. 
In the following sections, you can find a detailed response to each comment raised during the previous round of review.

# Editor comments

> "I agree that your manuscript is much improved and now only in need of relatively minor revisions. In addition to addressing the AE and reviewer's comments, please add terms related to invasive species to the keywords to aid in discoverability of your paper."

Many thanks the encouraging words. We have included 'invasive species' as a keyword. To make space for this keyworkd we have removed 'controllability' which is already highlighted as part of the title.

# Associate Editor's comments

### 2019-01-13 paper/manuscript.Rmd
Editor's comments

**Keywords:** Keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species' importance, control capacity, structural stability, controllability

>>>>

**Keywords:** Invasive species, keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species' importance, control capacity, structural stability
